---
title: 'HierFabs: installation'
author: "Xiao Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HierFabs: installation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
  
## Install the HierFabs
This vignette provides an introduction to the R package `HierFabs`, where the function `HierFabs` implements our model. With the completely newly developed forward and backward steps to accommodate hierarchy, `HierFabs` is able to detect important main effects and interactions under both the strong and weak hierarchy. Advancing from the existing studies, `HierFabs` accommodates multiple types of interaction models with differentiable loss functions under a unified framework. 
The package can be installed with the following command from [Github](https://github.com/XiaoZhangryy/HierFabs):

```{r  eval=FALSE}
install.packages('devtools')
devtools::install_github("XiaoZhangryy/HierFabs")
```

The package can be loaded with the command:
```{r  eval=FALSE}
library("HierFabs")
```












## Session information
```{r  eval = TRUE}
sessionInfo()
```